Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-19 paper/paper.tex
reverting last commit
update table 2 and 3

\begin{figure}[h]
  \vspace{-2ex}
  \lstinputlisting[language=C,numbers=none,frame=none,keywords={flags,threshold,window,icmp\_id,icmp\_seq}]{synflood-top5-rules.suricata}
  \vspace{-3ex}  
\end{figure}

@@

    JBoss JMX\MyComment{ Console Beanshell Exploit} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & - & TCP \MyComment{& Local File Inclusion} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{Privilege Escalation} & - & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    - & - & HTTP \MyComment{& \Luc{Adicionar}} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    \bottomrule
  \end{tabular}
\end{table*}

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \centering
  \begin{tabular}{lllp{9cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{\#~Rules created} &
    \multicolumn{1}{c}{Rank} \\
    \midrule
    Ping Scan & - & - \\
    SYN Flood & - & - \\
    JBoss JMX & - & - \\
    WeBid & - & - \\    
    ColdFusion & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\Mar{listem 5 primeira regras neste caso}

@@

    JBoss JMX\MyComment{ Console Beanshell Exploit} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & - & TCP \MyComment{& Local File Inclusion} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{Privilege Escalation} & - & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    \bottomrule
  \end{tabular}
\end{table*}

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \centering
  \begin{tabular}{lllp{9cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{\#~Rules created} &
    \multicolumn{1}{c}{Rank} \\
    \midrule
    Ping Scan & - & - \\
    SYN Flood & - & - \\
    JBoss JMX & 283 & 19 \\
    WeBid & - & - \\    
    ColdFusion & 566 & 37 \\
    .htaccess access & 572 & 1 \\
    .idq access & 700 & 136 \\
    iisadmin access & 502 & 117 \\
    /system32/ in URI & 1060 & 191 \\
    Script tag in URI & 1332 & 304 \\
    \bottomrule
  \end{tabular}
\end{table}
